Finding shortest and closest vectors in a lattice of Voronoi's first kind

### 2014-04-21 talk/presentation.tex
minor

\begin{itemize}
\item This is called the \term{closest lattice point problem} and a solution is called a \term{closest lattice point} to $y$.
\end{itemize}

@@

\frame{
\frametitle{The closest lattice point problem}
\begin{itemize}
\item The lattice point $x \in \Lambda$ is closest to $y \in \reals^m$ if and only if
\[
y \in \vor(\Lambda) + x.
\]
\item Equivalently $x$ is closest to $y$ if and only if
\[
\dotprod{(y - x)}{v} \leq \tfrac{1}{2} \dotprod{v}{v}
\]
for all $v \in \relevant(\Lambda)$.
\end{itemize}
}

@@

\frame{
\frametitle{A series of relevant vectors}
For a lattice of Voronoi's first kind:
\begin{itemize}
\item The intial point $x_0$ can be chosen to ensure that at most $K = n$ iterations is required before a closest point in found.
\item Minimisation over the set of relevant vector can be performed by computing a minimimum cut in a flow network.
\item Using known algorithms a minimum cut can be found in $O(n^3)$ operations.
\item In total $O(n^4)$ operations are required to compute a closest lattice point.
\end{itemize}
}

\frame{
\frametitle{A series of relevant vectors}
{\color{gray}For a lattice of Voronoi's first kind:}
\begin{itemize}
\item The intial point $x_0$ can be chosen to ensure that at most $K = n$ iterations is required before a closest point in found.
\item {\color{gray}Minimisation over the set of relevant vector can be performed by computing a minimimum cut in a flow network.}
\item {\color{gray}Using known algorithms a minimum cut can be found in $O(n^3)$ operations.}
\item {\color{gray}In total $O(n^4)$ operations are required to compute a closest lattice point.}
\end{itemize}
}

@@

\begin{itemize}
\item Can good codes or quantisers be constructed from lattices of Voronoi's first kind?
\item Do applications, such as global position, phase unwrapping, circular statistics, involve lattices of Voronoi's first kind?
\end{itemize}

>>>>

\begin{itemize}
\item This is called the \term{closest lattice point problem} and a solution is called a \term{closest lattice point} to $y$.
\item The lattice point $x \in \Lambda$ is closest to $y \in \reals^m$ if and only if
\[
y \in \vor(\Lambda) + x.
\]
\end{itemize}

@@

% \frame{
% \frametitle{The closest lattice point problem}
% \begin{itemize}
% \item Equivalently $x$ is closest to $y$ if and only if
% \[
% \dotprod{(y - x)}{v} \leq \tfrac{1}{2} \dotprod{v}{v}
% \]
% for all $v \in \relevant(\Lambda)$.
% \end{itemize}
% }

@@

\frame{
\frametitle{A series of relevant vectors}
For a lattice of Voronoi's first kind:
\begin{itemize}
\item $x_0$ can be chosen to ensure that a closest lattice point in found after at most $K \leq n$ iterations.
\item Minimisation over the set of relevant vector can be performed by computing a minimimum cut in a flow network.
\item Using known algorithms a minimum cut can be found in $O(n^3)$ operations.
\item In total $O(n^4)$ operations are required to compute a closest lattice point.
\end{itemize}
}

\begin{theorem}
Let $\Lambda$ be a $n$-dimensional lattice of Voronoi's first kind with obtuse superbase $b_1, \dots, b_{n+1}$.  Let $z_1,\dots,z_{n+1} \in \reals$ minimise
\[
\| y - \sum_{n=1}^{n+1} b_i z_i \| 
\]
and put
\[
x_0 = \sum_{n=1}^{n+1} b_i \floor{z_i}.
\]
The iterative proceedure, initialized at $x_0$, converges to a closest lattice point in at most $K \leq n$ iterations.
\end{theorem}
}

@@

\begin{itemize}
\item Can good codes or quantisers be constructed from lattices of Voronoi's first kind?
\item Do applications such as global position, phase unwrapping, circular statistics, etc., involve lattices of Voronoi's first kind?
\end{itemize}
